Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
rephrase and minor

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                     Handling Semantic Gap  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Generating a unified FW-HW model for co-verification is a 
well-known phenomenon to handle the semantic mismatch between the 
HW~\footnote{Note that whenever we refer to ``hardware'' 
from this point onwards, we mean an RTL implementation 
and not a TLM.}  and FW models.  Most of the existing techniques 
in~\cite{fmsd02,emsoft07,fase10} for constructing a unified FW-HW model are not 
useful in practise for three reasons -- 1) use of abstract HW models 
instead of register-transfer level implementation, 2) the HW-FW model
construction is agnostic to the underlying reasoning engine, and 3) 
does not leverage the property specification over HW-FW boundary, hence 
ineffective for practical co-verification.  We will call the unified FW-HW 
model as \emph{co-verification model}.

@@

A desirable characteristic of a co-verification model is the ability to exploit 
the expressivity of the underlying reasoning engines.  To this end, \hwcbmcv
constructs either a bit-level co-verification model that are checked with a SAT solvers 
or a word-level model that are checked with SMT solvers.  Whereas, a 
co-verification model in \verifox is constructed 
by first translating the RTL description into a software representation in C,
called \emph{software netlist}, which is then followed by sequentializing the FW 
model and the software netlist model.  This results in a single
threaded sequential co-verification model which is represented in C. A path-wise 
symbolic execution is then performed over the co-verification model to
automatically mine relevant interaction behaviors between the FW and HW models.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                     Handling Semantic Gap  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Generating a unified FW-HW model for co-verification is a 
well-known phenomenon to handle the semantic mismatch between  
HW~\footnote{Note that whenever we refer to ``hardware'' 
from this point onwards, we mean an RTL implementation 
and not a TLM.}  and FW models.  Most of the existing techniques 
in~\cite{fmsd02,emsoft07,fase10} for constructing a unified FW-HW model are not 
useful in practise for three reasons -- 1) use of abstract HW models 
instead of RTL implementation, 2) the HW-FW model
construction is agnostic to the underlying reasoning engine, and 3) 
it does not leverage the property specification over HW-FW boundary, hence 
ineffective for practical co-verification.  We will call the unified FW-HW 
model as \emph{co-verification model}.

@@

A desirable characteristic of a co-verification model is the ability to exploit 
the expressiveness of the underlying reasoning engines.  To this end, \hwcbmcv
constructs either a bit-level co-verification model that is checked with a SAT solver 
or a word-level model that is checked with an SMT solver.  Whereas, a 
co-verification model in \verifox is constructed 
by first translating the RTL description into a software representation in C,
called \emph{software netlist}, which is then followed by sequentializing the FW 
model and the software netlist model.  This results in a single
threaded sequential co-verification model which is represented in C. A path-wise 
symbolic execution is then performed over the co-verification model to
automatically mine relevant interactions between the FW and HW models.
